Data Preparation, Integration and Cleaning

### 2017-10-23 abbDataPrep_Script.Rmd
co
Add:  Seasonality sensitivity test prep

@@

  library(spdep)
  library(maptools)
  library(gstat)
  library(ggplot2)
  library(geosphere)
  library(ggmap)
  library(xtable)
  library(chron)
  library(plyr)
  library(sp)
  library(rgeos)
  library(reshape2)
  library(stringr)
  library(RColorBrewer)
  library(Hmisc)

@@

  comp.name <- Sys.info()['nodename']

  # Assign path based on computer name

  if(comp.name == '7020D-121777-W' | comp.name == 'DESKTOP-1D7JO4J'){

@@

    data.path <- 'alternate data path'
    code.path <- 'alternate data path'
    fig.path <- 'alternate data path'

@@

  source(paste0(code.path, '/dataVizTools/ggPlotTools.R'))
  source(paste0(code.path, '/datamgmttools/dataMungeTools.R'))
  source(paste0(code.path, '/spatialTools/spatialLogitModels.R'))
  source(paste0(code.path, '/spatialTools/point2surface_Tools.R'))

@@

  str.data <- str.data[, str.keep.flds]

@@

  names(str.data) <- c('property.id', 'host.id', 'listing.title', 'property.type',
                       'listing.type', 'created.date', 'latitude', 'longitude',
                       'average.daily.rate', 'overall.rating',
                       'max.guests', 'cancel.policy', 'cleaning.fee',
                       'nightly.rate', 'weekly.rate', 'monthly.rate', 'min.stay',
                       'bedrooms', 'baths', 'min.date', 'max.date', 'total.days',
                       'block.rate', 'avail.rate', 'longest.block', 'nbr.block', 
                       'med.block', 'created.year')

@@

  str.data <- str.data[(str.data$max.date - str.data$min.date) >= 178, ]
  str.data <- str.data[str.data$max.date >= '2016-03-01' &
                         str.data$min.date <= '2016-03-01', ]

  daily.data <- daily.data[daily.data$date >= '2015-09-01', ]

@@

  ltr.data <- ltr.data[ltr.data$event.date >= '2014-09-01' & 
                            ltr.data$event.date <= '2015-08-31', ]
  listing.data <- listing.data[listing.data$id.key %in% ltr.data$id.key, ]

@@

  str.data$str.month <- 1
  daily.data$str.month <- as.numeric(as.factor(substr(daily.data$date, 1, 7)))

@@

  str.data$type <- 'Other'
  str.data$type[str.data$property.type %in% c('Apartment', 'Condominium')] <- 'Apartment'
  str.data$type[str.data$property.type %in% c('House', 'Townhouse')] <- 'House'

@@

  str.types <- ggplot(str.data, aes(x=type)) + 
    geom_bar(color=str.col, fill=str.col) +
    xlab('\nProperty Type\n') + 
    ggtitle('\nShort Term Rentals\n')  +
    ylab('# of Properties\n') +
    theme(plot.title = element_text(hjust = 0.5))

@@

  str.data <- subset(str.data, type != 'Other')
  ltr.data <- subset(ltr.data, type != 'Other')

@@

  # Fix data types and names
  str.data$listing.type <- as.character(str.data$listing.type)
  str.data$listing.type[str.data$listing.type == 'Entire home/apt'] <- 'Entire home'

  list.types <- ggplot(str.data, aes(x=listing.type)) + 
      geom_bar(color=str.col, fill=str.col) +
      xlab('\nListing Type\n') + 
      ggtitle('\nShort Term Rentals by Listing Type\n')  +
      ylab('# of Properties\n') +
    theme(plot.title = element_text(hjust = 0.5))

@@

  str.data <- str.data[str.data$listing.type == 'Entire home', ]

@@

  # Short term data
  str.data <- str.data[!is.na(str.data$bedrooms), ]
  str.data <- str.data[str.data$bedrooms <= 10, ]

@@

  strbed <- ggplot(str.data, aes(x=bedrooms)) + 
    geom_bar(fill=str.col, color=str.col) +
    facet_wrap(~type,scales='free_y') +
    scale_x_continuous(labels=0:10, breaks=0:10) +
    xlab('\nBedrooms\n') +
    ylab('') +
    ggtitle('Bedrooms in Short Term Rentals') +
    theme(plot.title = element_text(hjust = 0.5))

@@

  str.data <- str.data[str.data$bedrooms < 5, ]
  ltr.data <- ltr.data[ltr.data$bedrooms < 5, ]

@@

  str.id <- which(str.data$bedrooms > 3 & str.data$type =='Apartment')
  ltr.id <- which(ltr.data$bedrooms > 3 & ltr.data$type =='Apartment')

  if(length(str.id) > 0) str.data <- str.data[-str.id, ]
  if(length(ltr.id) > 0) ltr.data <- ltr.data[-ltr.id, ]

  # Convert 0 Bed to 1 Bed  
  str.data$bedrooms[str.data$bedrooms == 0] <- 1

@@

  ltr.data <- ltr.data[!is.na(ltr.data$baths), ]
  str.data <- str.data[!is.na(str.data$baths), ]

@@

  stbath <- ggplot(str.data, aes(x=baths)) + 
    geom_bar(fill=str.col, color=str.col) +
    facet_wrap(~type, scales='free_y') +
    scale_x_continuous(labels=0:8, breaks=0:8)+
    xlab('\nBathrooms\n') +
    ylab('') + 
    ggtitle('Bathrooms in Short Term ltrals') +
    theme(plot.title = element_text(hjust = 0.5))

@@

  # Short term data
  str.data <- str.data[str.data$baths < 4, ]
  str.data <- str.data[str.data$baths > 0, ]

@@

  str.data$baths <- round(str.data$baths + .01, 0)

@@

  ltr.data$bedbath <- paste0(ltr.data$bedrooms, '..', ltr.data$baths)
  str.data$bedbath <- paste0(str.data$bedrooms, '..', str.data$baths)

@@

  stbb <- ggplot(str.data, aes(x=bedbath)) +
    geom_bar(fill=str.col, color=str.col) + 
    xlab('\nBed/Bath Combo\n') +
    ylab('Number of Properties\n') +
    ggtitle('Short Term Rentals') + 
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    facet_wrap(~type, scales='free_y')+
    theme(plot.title = element_text(hjust = 0.5))

@@

  ltr.data <- ltr.data[ltr.data$bedbath %in% acc.bb, ]
  str.data <- str.data[str.data$bedbath %in% acc.bb, ]

@@

  str.data$bedbath <- factor(str.data$bedbath, 
                              levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
  ltr.data$bedbath <- factor(ltr.data$bedbath, 
                               levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))

@@

  str.data$product <- paste0(substr(str.data$type, 1, 1), str.data$bedbath)
  ltr.data$product <- paste0(substr(ltr.data$type, 1, 1), ltr.data$bedbath)

@@

  ltr.data <- ltr.data[!is.na(ltr.data$event.price), ]
  str.data <- str.data[!is.na(str.data$nightly.rate), ]

@@

  str.data$average.daily.rate <- str.data$average.daily.rate * exch.rate
  str.data$nightly.rate <- str.data$nightly.rate * exch.rate
  str.data$weekly.rate <- str.data$weekly.rate * exch.rate
  str.data$monthly.rate <- str.data$monthly * exch.rate

@@

  daily.data$price <- daily.data$price * exch.rate

@@

   # Get all of the reservations
  resv.daily <- daily.data[daily.data$status == 'R', ]

@@

  # Add median rate to the property  
  str.data$med.rate <- med.daily$Var[match(str.data$property.id, med.daily$ID)]

  # Remove those with no valid median rate
  str.data <- str.data[!is.na(str.data$med.rate), ]

@@

  # Nightly Rate plot
  rate.plot <- ggplot(str.data, aes(x=nightly.rate)) + 
    geom_density(fill=str.col, alpha=.8) + 
    ylab('') +
    xlab('Nightly Rate') +
    ggtitle('Short Term Rentals') + 
    scale_x_continuous(limits=c(0, 600)) +
    theme(axis.title.y=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y=element_blank()) +
    theme(plot.title = element_text(hjust = 0.5))

@@

  str.data <- str.data[str.data$med.rate >= 50 &
                         str.data$med.rate <= 500, ]

@@

  str.data$bookings <- round(str.data$total.days * 
                               (1 - (str.data$block.rate + str.data$avail.rate)), 0)

@@

  str.data <- str.data[str.data$bookings > 0, ]

  str.data$gross.revenue <- (str.data$bookings * str.data$med.rate) 
  ltr.data$gross.revenue <- ltr.data$event.price * (52 - ltr.data$dom / 7)

  str.small <- str.data[,c('baths', 'gross.revenue')]
  str.small$tenure <- 'short-term'
  ltr.small <- ltr.data[,c('baths', 'gross.revenue')]
  ltr.small$tenure <- 'long-term'
  all.small <- rbind(str.small, ltr.small)

@@

  latMid <- median(str.data$latitude)
  longMid <- median(str.data$longitude)

@@

  # Convert to point shapefile
  str.prop.shp <- SpatialPointsDataFrame(cbind(str.data$longitude,
                                               str.data$latitude),
                                         str.data,
                                         proj4string=CRS("+init=epsg:4283"))

  # Add suburb name 
  spJoin <- over(str.prop.shp, suburbs.shp)
  str.data$suburb <- as.character(spJoin$name_2006)
  str.data$suburb[is.na(str.data$suburb)] <- 'missing'

  # Add suburb designation
  str.data$sub.class <- as.character(spJoin$suburbdesi)
  str.data$sub.class[is.na(str.data$sub.class)] <- 'missing'

  # Add SA1 designation
  spJoin <- over(str.prop.shp, sa1s.shp)
  str.data$sa1 <- spJoin$sa1_main11

  ## Add Beach Designation
  spJoin <- over(str.prop.shp, beach.buffer)
  str.data$beach <- ifelse(is.na(spJoin), 0 ,1)

  # Remove those missing a suburb classification (out of area)
  str.data <- str.data[str.data$sub.class != 'missing', ]
  str.data <- str.data[str.data$sa1 != 'missing', ]

@@

  # Add individual classes
  str.data$geo.mrkt <- 'rural'
  str.data$geo.mrkt[str.data$sub.class == 'Middle'] <- 'suburban'
  str.data$geo.mrkt[str.data$sub.class == 'Inner'] <- 'city'
  str.data$geo.mrkt[str.data$suburb %in% core.suburbs] <- 'city-core'
  str.data$geo.mrkt[str.data$beach == 1] <- 'beach'

  # Order the factors properly
  str.data$geo.mrkt <- factor(str.data$geo.mrkt, 
                              levels=c('city-core', 'city', 'suburban', 
                                        'rural', 'beach'))

@@

  str.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
    geom_point(data=str.data, aes(x=longitude, y=latitude, color=geo.mrkt), size=.2,
               alpha=.2) +
    scale_color_manual(values=sm.col) +
    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
    xlab('') + ylab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "white"),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
    guides(colour = guide_legend(override.aes = list(size=3,
                                                     alpha=1))) + 
    ggtitle('Short-Term Rental Locations')+
    theme(plot.title = element_text(hjust = 0.5))

@@

  strtype.map <- ggplot() +
    geom_bar(data=str.data, aes(x=geo.mrkt, fill=geo.mrkt)) +
    scale_fill_manual(values=sm.col) +
    facet_wrap(~type) +
    ylab('# of Properties\n') + xlab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank()) +
    #ggtitle('Short Term Property Type\nBy Submarket')+
    theme(plot.title = element_text(hjust = 0.5))

@@

  # Convert suburbs from factor to character
  str.data$suburb <- as.character(str.data$suburb)
  ltr.data$suburb <- as.character(ltr.data$suburb)

@@

  daily.data <- daily.data[daily.data$property.id %in% str.data$property.id,]

@@

 # Calculate the new daily summaries

 daily.summ.list <- lapply(as.list(str.data$property.id), abbCalcBookStr,
                            book.data=daily.data)
 daily.summ <- rbind.fill(daily.summ.list)
 daily.summ$min.date <- daily.summ$max.date <- NULL

 # Remove existing 
 cut.fields <- which(names(str.data) %in% c('total.days', 'block.rate', 'avail.rate',
                                     'longest.block', 'nbr.block', 'med.block'))
 str.data <- str.data[ ,-cut.fields]

 # Add summary data to property data
 str.data <- merge(str.data, 
                   daily.summ, 
                   by.x='property.id',
                   by.y='id')

@@

  cpmiss <- which(str.data$cancel.policy == '')
  str.data <- str.data[-cpmiss, ]

@@

  ss60 <- which(str.data$cancel.policy == 'Super Strict 60 Days')
  str.data$cancel.policy[ss60] <- 'Strict'

@@

  save(str.data, ltr.data, daily.data, listing.data, subs, abb.col, 
       beach.shp, core.suburbs, exch.rate, ltr.col, str.col, sa1s.shp, 
       suburbs.shp, study.suburbs, clean.count, daily.run.total, list.run.total,
       ltr.run.total, str.run.total,
       file=paste0(data.path, 'prepared/prep_workspace.RData'))

>>>>

&nbsp;
```{r set_dates}

  library(lubridate)
  data_name <- 'jun'
  strike_date <- lubridate::as_date('2015-06-01')

@@

  library(spdep)
  library(maptools)
  library(gstat)
  library(ggplot2)
  library(geosphere)
  library(ggmap)
  library(xtable)
  # library(chron)
  library(plyr)
  library(sp)
  library(rgeos)
  library(reshape2)
  library(stringr)
  library(RColorBrewer)
  library(Hmisc)
  library(dplyr)
  library(multidplyr)
  library(lubridate)

@@

@@

@@

  source(paste0(code.path, 'tools/dataVizTools/ggPlotTools.R'))
  source(paste0(code.path, 'tools/datamgmttools/dataMungeTools.R'))
  source(paste0(code.path, 'tools/spatialTools/spatialLogitModels.R'))
  source(paste0(code.path, 'tools/spatialTools/point2surface_Tools.R'))

@@

  str_df <- str_df[, str.keep.flds]

@@

  names(str_df) <- c('property.id', 'host.id', 'listing.title', 'property.type',
                       'listing.type', 'created.date', 'latitude', 'longitude',
                       'average.daily.rate', 'overall.rating',
                       'max.guests', 'cancel.policy', 'cleaning.fee',
                       'nightly.rate', 'weekly.rate', 'monthly.rate', 'min.stay',
                       'bedrooms', 'baths', 'min.date', 'max.date', 'total.days',
                       'block.rate', 'avail.rate', 'longest.block', 'nbr.block', 
                       'med.block', 'created.year')

@@

  str_df <- str_df[(str_df$max.date - str_df$min.date) >= 178, ]

  str_df <- str_df[str_df$max.date >= (strike_date + 182) &
                         str_df$min.date <= (strike_date + 182), ]

  daily_df <- daily_df[daily_df$date >= strike_date, ]

@@

  ltr.data <- ltr.data[ltr.data$event.date >= (strike_date - 365) & 
                            ltr.data$event.date <= (strike_date - 1), ]
  listing.data <- listing.data[listing.data$id.key %in% ltr.data$id.key, ]

@@

  str_df$str.month <- 1
  daily_df$str.month <- as.numeric(as.factor(substr(daily_df$date, 1, 7)))

@@

  str_df$type <- 'Other'
  str_df$type[str_df$property.type %in% c('Apartment', 'Condominium')] <- 'Apartment'
  str_df$type[str_df$property.type %in% c('House', 'Townhouse')] <- 'House'

@@

  str.types <- ggplot(str_df, aes(x=type)) + 
    geom_bar(color=str.col, fill=str.col) +
    xlab('\nProperty Type\n') + 
    ggtitle('\nShort Term Rentals\n')  +
    ylab('# of Properties\n') +
    theme(plot.title = element_text(hjust = 0.5))

@@

  str_df <- subset(str_df, type != 'Other')
  ltr.data <- subset(ltr.data, type != 'Other')

@@

  # Fix data types and names
  str_df$listing.type <- as.character(str_df$listing.type)
  str_df$listing.type[str_df$listing.type == 'Entire home/apt'] <- 'Entire home'

  list.types <- ggplot(str_df, aes(x=listing.type)) + 
      geom_bar(color=str.col, fill=str.col) +
      xlab('\nListing Type\n') + 
      ggtitle('\nShort Term Rentals by Listing Type\n')  +
      ylab('# of Properties\n') +
    theme(plot.title = element_text(hjust = 0.5))

@@

  str_df <- str_df[str_df$listing.type == 'Entire home', ]

@@

  # Short term data
  str_df <- str_df[!is.na(str_df$bedrooms), ]
  str_df <- str_df[str_df$bedrooms <= 10, ]

@@

  strbed <- ggplot(str_df, aes(x=bedrooms)) + 
    geom_bar(fill=str.col, color=str.col) +
    facet_wrap(~type,scales='free_y') +
    scale_x_continuous(labels=0:10, breaks=0:10) +
    xlab('\nBedrooms\n') +
    ylab('') +
    ggtitle('Bedrooms in Short Term Rentals') +
    theme(plot.title = element_text(hjust = 0.5))

@@

  str_df <- str_df[str_df$bedrooms < 5, ]
  ltr.data <- ltr.data[ltr.data$bedrooms < 5, ]

@@

  str.id <- which(str_df$bedrooms > 3 & str_df$type =='Apartment')
  ltr.id <- which(ltr.data$bedrooms > 3 & ltr.data$type =='Apartment')

  if(length(str.id) > 0) str_df <- str_df[-str.id, ]
  if(length(ltr.id) > 0) ltr.data <- ltr.data[-ltr.id, ]

  # Convert 0 Bed to 1 Bed  
  str_df$bedrooms[str_df$bedrooms == 0] <- 1

@@

  ltr.data <- ltr.data[!is.na(ltr.data$baths), ]
  str_df <- str_df[!is.na(str_df$baths), ]

@@

  stbath <- ggplot(str_df, aes(x=baths)) + 
    geom_bar(fill=str.col, color=str.col) +
    facet_wrap(~type, scales='free_y') +
    scale_x_continuous(labels=0:8, breaks=0:8)+
    xlab('\nBathrooms\n') +
    ylab('') + 
    ggtitle('Bathrooms in Short Term ltrals') +
    theme(plot.title = element_text(hjust = 0.5))

@@

  # Short term data
  str_df <- str_df[str_df$baths < 4, ]
  str_df <- str_df[str_df$baths > 0, ]

@@

  str_df$baths <- round(str_df$baths + .01, 0)

@@

  ltr.data$bedbath <- paste0(ltr.data$bedrooms, '..', ltr.data$baths)
  str_df$bedbath <- paste0(str_df$bedrooms, '..', str_df$baths)

@@

  stbb <- ggplot(str_df, aes(x=bedbath)) +
    geom_bar(fill=str.col, color=str.col) + 
    xlab('\nBed/Bath Combo\n') +
    ylab('Number of Properties\n') +
    ggtitle('Short Term Rentals') + 
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    facet_wrap(~type, scales='free_y')+
    theme(plot.title = element_text(hjust = 0.5))

@@

  ltr.data <- ltr.data[ltr.data$bedbath %in% acc.bb, ]
  str_df <- str_df[str_df$bedbath %in% acc.bb, ]

@@

  str_df$bedbath <- factor(str_df$bedbath, 
                              levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
  ltr.data$bedbath <- factor(ltr.data$bedbath, 
                               levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))

@@

  str_df$product <- paste0(substr(str_df$type, 1, 1), str_df$bedbath)
  ltr.data$product <- paste0(substr(ltr.data$type, 1, 1), ltr.data$bedbath)

@@

  ltr.data <- ltr.data[!is.na(ltr.data$event.price), ]
  str_df <- str_df[!is.na(str_df$nightly.rate), ]

@@

  str_df$average.daily.rate <- str_df$average.daily.rate * exch.rate
  str_df$nightly.rate <- str_df$nightly.rate * exch.rate
  str_df$weekly.rate <- str_df$weekly.rate * exch.rate
  str_df$monthly.rate <- str_df$monthly * exch.rate

@@

  daily_df$price <- daily_df$price * exch.rate

@@

   # Get all of the reservations
  resv.daily <- daily_df[daily_df$status == 'R', ]

@@

  # Add median rate to the property  
  str_df$med.rate <- med.daily$Var[match(str_df$property.id, med.daily$ID)]

  # Remove those with no valid median rate
  str_df <- str_df[!is.na(str_df$med.rate), ]

@@

  # Nightly Rate plot
  rate.plot <- ggplot(str_df, aes(x=nightly.rate)) + 
    geom_density(fill=str.col, alpha=.8) + 
    ylab('') +
    xlab('Nightly Rate') +
    ggtitle('Short Term Rentals') + 
    scale_x_continuous(limits=c(0, 600)) +
    theme(axis.title.y=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y=element_blank()) +
    theme(plot.title = element_text(hjust = 0.5))

@@

  str_df <- str_df[str_df$med.rate >= 50 &
                         str_df$med.rate <= 500, ]

@@

  str_df$bookings <- round(str_df$total.days * 
                               (1 - (str_df$block.rate + str_df$avail.rate)), 0)

@@

  str_df <- str_df[str_df$bookings > 0, ]

  str_df$gross.revenue <- (str_df$bookings * str_df$med.rate) 
  ltr.data$gross.revenue <- ltr.data$event.price * (52 - ltr.data$dom / 7)

  str.small <- str_df[,c('baths', 'gross.revenue')]
  str.small$tenure <- 'short-term'
  ltr.small <- ltr.data[,c('baths', 'gross.revenue')]
  ltr.small$tenure <- 'long-term'
  all.small <- rbind(str.small, ltr.small)

@@

  latMid <- median(str_df$latitude)
  longMid <- median(str_df$longitude)

@@

  # Convert to point shapefile
  str.prop.shp <- SpatialPointsDataFrame(cbind(str_df$longitude,
                                               str_df$latitude),
                                         str_df,
                                         proj4string=CRS("+init=epsg:4283"))

  # Add suburb name 
  spJoin <- over(str.prop.shp, suburbs.shp)
  str_df$suburb <- as.character(spJoin$name_2006)
  str_df$suburb[is.na(str_df$suburb)] <- 'missing'

  # Add suburb designation
  str_df$sub.class <- as.character(spJoin$suburbdesi)
  str_df$sub.class[is.na(str_df$sub.class)] <- 'missing'

  # Add SA1 designation
  spJoin <- over(str.prop.shp, sa1s.shp)
  str_df$sa1 <- spJoin$sa1_main11

  ## Add Beach Designation
  spJoin <- over(str.prop.shp, beach.buffer)
  str_df$beach <- ifelse(is.na(spJoin), 0 ,1)

  # Remove those missing a suburb classification (out of area)
  str_df <- str_df[str_df$sub.class != 'missing', ]
  str_df <- str_df[str_df$sa1 != 'missing', ]

@@

  # Add individual classes
  str_df$geo.mrkt <- 'rural'
  str_df$geo.mrkt[str_df$sub.class == 'Middle'] <- 'suburban'
  str_df$geo.mrkt[str_df$sub.class == 'Inner'] <- 'city'
  str_df$geo.mrkt[str_df$suburb %in% core.suburbs] <- 'city-core'
  str_df$geo.mrkt[str_df$beach == 1] <- 'beach'

  # Order the factors properly
  str_df$geo.mrkt <- factor(str_df$geo.mrkt, 
                              levels=c('city-core', 'city', 'suburban', 
                                        'rural', 'beach'))

@@

  str.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
    geom_point(data=str_df, aes(x=longitude, y=latitude, color=geo.mrkt), size=.2,
               alpha=.2) +
    scale_color_manual(values=sm.col) +
    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
    xlab('') + ylab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "white"),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
    guides(colour = guide_legend(override.aes = list(size=3,
                                                     alpha=1))) + 
    ggtitle('Short-Term Rental Locations')+
    theme(plot.title = element_text(hjust = 0.5))

@@

  strtype.map <- ggplot() +
    geom_bar(data=str_df, aes(x=geo.mrkt, fill=geo.mrkt)) +
    scale_fill_manual(values=sm.col) +
    facet_wrap(~type) +
    ylab('# of Properties\n') + xlab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank()) +
    #ggtitle('Short Term Property Type\nBy Submarket')+
    theme(plot.title = element_text(hjust = 0.5))

@@

  # Convert suburbs from factor to character
  str_df$suburb <- as.character(str_df$suburb)
  ltr.data$suburb <- as.character(ltr.data$suburb)

@@

  daily_df <- daily_df[daily_df$property.id %in% str_df$property.id,]

@@

    # Create new cluster
  abb_cl <- get_default_cluster()

  # Register function and variable
  cluster_copy(abb_cl, abbCalcBookStr)

  # Summarize daily by property
  daily_summ <- daily_df %>% 
    multidplyr::partition(property.id, cluster=abb_cl) %>% 
    dplyr::do(abbCalcBookStr(.)) %>% 
    dplyr::collect()

 # Remove existing 
 str_df <- str_df %>%
   dplyr::select(-c(total.days, block.rate, avail.rate, longest.block, nbr.block,
                    med.block, bookings))

 # Add summary data to property data
 str_df <- str_df %>% dplyr::left_join(daily_summ, by='property.id')

@@

  str_df <- str_df %>% 
    dplyr::filter(cancel.policy %in% c('Flexible', 'Moderate', 'Strict'))

@@

  ss60 <- which(str_df$cancel.policy == 'Super Strict 60 Days')
  str_df$cancel.policy[ss60] <- 'Strict'

@@

  save(str_df, ltr.data, daily_df, listing.data, subs, abb.col, 
       beach.shp, core.suburbs, exch.rate, ltr.col, str.col, sa1s.shp, 
       suburbs.shp, study.suburbs, clean.count, daily.run.total, list.run.total,
       ltr.run.total, str.run.total,
       file=paste0(data.path, 'prepared/prep_workspace_', data_name, '.RData'))
